Milestone 2: Core results 01

### 2023-03-26 R_codeP01/reports/MS2_report03_truncated.Rmd
report writing

# Lasso - Bootstrap
### 6 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_prolif.RData")
l_b_6_p <- report02_out(lb_obj_6_prolif)
```

### 6 genes -> ROR_proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_RORprolif.RData")
l_b_6_ROR_p <- report02_out(lb_obj_6_RORprolif)
```

### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
l_b_771_p <- report02_out(lb_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
l_b_771_ROR_p <- report02_out(lb_obj_771_RORprolif)
```

### node values -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_prolif.RData")
l_b_nodes_p <- report02_out(lb_obj_nodes_prolif)
```

### node values -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_RORprolif.RData")
l_b_nodes_ROR_p <- report02_out(lb_obj_nodes_RORprolif)
```

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
```

### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
```

### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
```

### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
```

@@

### 6 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
l_c_6_p <- report02_out(lc_obj_6_prolif)
```
### 6 genes -> ROR_proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
```

### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
l_c_771_p <- report02_out(lc_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
```

### node values -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
```

### node values -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
```

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
```

### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
```

### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
```

### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
```

@@

# Ridge bootstrap
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RData")
r_b_771_p <- report02_out_ridge(r_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_p.RData")
r_b_771_ROR_p <- report02_out_ridge(r_b_obj_771_ROR_p)
```

# Ridge repeated cross-validation
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
r_c_771_p <- report02_out_ridge(r_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
r_c_771_ROR_p <- report02_out_ridge(r_c_obj_771_RORprolif)
```

@@

# Elastic Net - bootstrap
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
e_b_771_p <- report02_out_ridge(e_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
e_b_771_ROR_p <- report02_out_ridge(e_b_obj_771_ROR_p)
```

# Elastic Net: cross-validation
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prolif.RData")
e_c_771_p <- report02_out_ridge(e_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
e_c_771_ROR_p <- report02_out_ridge(e_c_obj_771_RORprolif)
```

@@

# Boosting with stumps as base learner - bootstrap
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
xg_b_771_p <- report02_out_ridge(xg_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
xg_b_771_ROR_p <- report02_out_ridge(xg_b_obj_771_ROR_p)
```

# Boosting with stumps as base learner cross-validation
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
xg_c_771_p <- report02_out_ridge(xg_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_RORprolif.RData")
xg_c_771_ROR_p <- report02_out_ridge(xg_c_obj_771_RORprolif)
```

>>>>

# Lasso - Bootstrap
### 6 genes -> proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_prolif.RData")
l_b_6_p <- report02_out(lb_obj_6_prolif)
```

### 6 genes -> ROR_proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_6_RORprolif.RData")
l_b_6_ROR_p <- report02_out(lb_obj_6_RORprolif)
```

### 771 genes -> proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_prolif.RData")
l_b_771_p <- report02_out(lb_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_771_RORprolif.RData")
l_b_771_ROR_p <- report02_out(lb_obj_771_RORprolif)
```

### node values -> proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_prolif.RData")
l_b_nodes_p <- report02_out(lb_obj_nodes_prolif)
```

### node values -> ROR-proliferation score (lasso - bootstrap) 
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_nodes_RORprolif.RData")
l_b_nodes_ROR_p <- report02_out(lb_obj_nodes_RORprolif)
```

### Mechanistic + Residuals (additive) -> proliferation score  (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
```

### Mechanistic + Residuals (multiplicative) -> proliferation score   (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
```

### Mechnaistic + Residuals (additive) -> ROR-proliferation score  (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
```

### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
```

@@

### 6 genes -> proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_prolif.RData")
l_c_6_p <- report02_out(lc_obj_6_prolif)
```
### 6 genes -> ROR_proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_6_RORprolif.RData")
l_c_6_ROR_p <- report02_out(lc_obj_6_RORprolif)
```

### 771 genes -> proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_prolif.RData")
l_c_771_p <- report02_out(lc_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_771_RORprolif.RData")
l_c_771_ROR_p <- report02_out(lc_obj_771_RORprolif)
```

### node values -> proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_prolif.RData")
l_c_nodes_p <- report02_out(lc_obj_nodes_prolif)
```

### node values -> ROR-proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_nodes_RORprolif.RData")
l_c_nodes_ROR_p <- report02_out(lc_obj_nodes_RORprolif)
```

### Mechanistic + Residuals (additive) -> proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
```

### Mechanistic + Residuals (multiplicative) -> proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
```

### Mechnaistic + Residuals (additive) -> ROR-proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
```

### Mechnaistic + Residuals (multiplicative) -> ROR-proliferation score (lasso - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
```

@@

# Ridge bootstrap
### 771 genes -> proliferation score (ridge bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RData")
r_b_771_p <- report02_out_ridge(r_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score (ridge bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_p.RData")
r_b_771_ROR_p <- report02_out_ridge(r_b_obj_771_ROR_p)
```

# Ridge repeated cross-validation
### 771 genes -> proliferation score (ridge repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
r_c_771_p <- report02_out_ridge(r_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score (ridge repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_771_RORprolif.RData")
r_c_771_ROR_p <- report02_out_ridge(r_c_771_RORprolif)
```

@@

# Elastic Net - bootstrap
### 771 genes -> proliferation score (elastic Net - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
e_b_771_p <- report02_out_ridge(e_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score (elastic Net - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
e_b_771_ROR_p <- report02_out_ridge(e_b_obj_771_ROR_p)
```

# Elastic Net: cross-validation
### 771 genes -> proliferation score  (elastic Net - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prolif.RData")
e_c_771_p <- report02_out_ridge(e_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score  (elastic Net - repeated cross-validation)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
e_c_771_ROR_p <- report02_out_ridge(e_c_obj_771_RORprolif)
```

@@

# Boosting with stumps as base learner - bootstrap
### 771 genes -> proliferation score (boosting - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_p.RData")
xg_b_771_p <- report02_out_ridge(xg_b_obj_771_p)
```

### 771 genes -> ROR-proliferation score  (boosting - bootstrap)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_b_obj_771_ROR_p.RData")
xg_b_771_ROR_p <- report02_out_ridge(xg_b_obj_771_ROR_p)
```

# Boosting with stumps as base learner cross-validation
### 771 genes -> proliferation score  (boosting - rep cross-val)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_prolif.RData")
xg_c_771_p <- report02_out_ridge(xg_c_obj_771_prolif)
```

### 771 genes -> ROR-proliferation score   (boosting - rep cross-val)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/xg_c_obj_771_RORprolif.RData")
xg_c_771_ROR_p <- report02_out_ridge(xg_c_obj_771_RORprolif)
```
